### 2014-05-15 latex/paper1.tex
minor spellcheck/other changes

At the turn of the 20th century, physics had progressed to the point
where it was now possible to investigate the structure of matter and
light. Electromagnetic theory had been developed so that physicists
could investigate the charged particles making up the atom. Statistical
mechanics, originally developed to explain heat and gases, would help
Planck and Einstein realize the corpuscular nature of light. Physics was
ready for a major transformation. In the past, physics had been
primarily concerned with the behavior and motion of things, such as the
motion of planets, the behavior of light, the behavior of electric and
magnetic fields, or the behavior of heat and gases. In this paper, I
argue that at the turn of the 20th century, physics shifted from being
mainly concerned with the behavior of matter and light to being
interested in the actual structure of matter and light. Physicists
became interested in what made up the the things they were studying,
what was inside the atom, what was light made of, and physicists finally
had the tools they needed to find answers to these questions. I will
use the investigations into radioactivity, Thomson's discovery of the
electron, Zeeman's experiments, and Planck and Einstein's ideas about
light to illustrate the heightened interest in the structure of matter
of light during this time period.

Wilhelm R\"ontgen, in 1895, discovered X-rays, a new kind of ray that
penetrates many substances including human flesh. Inspired by
R\"ontgen's discovery, Henri Becquerel and Marie and Pierre Curie began
investigations in radioactive substances and the various rays those
substances produced. They found that radioactive substances would
spontaneously emit energetic rays and would not require an outside
source of energy to do this. These discoveries made physicists wonder
what was it about the structure of matter that allowed these rays to be
created, and also created interest in the composition of the emitted
rays.

@@

Thomson's discovery of what made up cathode rays was considered very
important at the time, and he was awarded the Nobel Prize in Physics in
1906 for his efforts. The discovery of the electron also helped to fuel
futher interest in the structure of matter. Thomson later proposed the
plum pudding model of the atom which had electrons embedded in a sea of
positive charge.

>>>>

At the turn of the 20th century, physics had progressed to the point
where it was now possible to investigate the structure of matter and
light. Electromagnetic theory had been developed so that physicists
could investigate the charged particles making up the atom. Statistical
mechanics, originally developed to explain heat and gases, would help
Planck and Einstein realize the corpuscular nature of light. Physics was
ready for a major transformation. In the past, physics had been
primarily concerned with the behavior and motion of things, such as the
motion of planets, the behavior of light, the behavior of electric and
magnetic fields, or the behavior of heat and gases. In this paper, I
argue that at the turn of the 20th century, physics shifted from being
mainly concerned with the behavior of matter and light to being
interested in the actual \textit{structure} of matter and light.
Physicists became interested in what made up the the things they were
studying, what was inside the atom, what was light made of, and
physicists finally had the tools they needed to find answers to these
questions. I will use the investigations into radioactivity, Thomson's
discovery of the electron, Zeeman's experiments, and Planck and
Einstein's ideas about light to illustrate the heightened interest in
the structure of matter of light during this time period.

Wilhelm R\"ontgen, in 1895, discovered X-rays, a new kind of ray that
penetrates many substances including human flesh. Inspired by
R\"ontgen's discovery, Henri Becquerel and Marie and Pierre Curie began
investigations into radioactive substances and the various rays those
substances produced. They found that radioactive substances would
spontaneously emit energetic rays and would not require an outside
source of energy to do this. These discoveries made physicists wonder
what was it about the structure of matter that allowed these rays to be
created, and also created interest in the composition of the emitted
rays.

@@

Thomson's discovery of what made up cathode rays was considered very
important at the time, and he was awarded the Nobel Prize in Physics in
1906 for his efforts. The discovery of the electron also helped to fuel
further interest in the structure of matter. Thomson later proposed the
plum pudding model of the atom which had electrons embedded in a sea of
positive charge.
